Segregation in Vienna's primary schools?

### 2021-01-15 _post/2020-03-02-primary-schools-in-vienna/primary-schools-in-vienna.Rmd
reformated post bih voting hor

---
title: "Segregation in Vienna's primary schools?"
description: |
  Drawing on public data from Vienna's school administration I look at how many percentages of pupils in each primary schoos subsequently leave for schools offering eventually a higher education entrance qualification (Matura). The main interest is in contrasting these ratios between closely (geo-)located schools.

>>>>

---
title: "Segregation in Vienna's primary schools?"
description: |
  Drawing on public data from Vienna's school administration I look at how many percentages of pupils in each primary school subsequently leave for schools offering eventually a higher education entrance qualification (Matura). The main interest is in contrasting these ratios between closely (geo-)located schools.
